---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hcesR

<!-- badges: start -->
<!-- badges: end -->

The goal of hcesR is to create a package that will help with the analysis of the Household Consumption Expenditure Survey (HCES) data. The package will contain functions that will help with the analysis of the data. The package will also contain a dataset that will be used to demonstrate the use of the functions in the package. The package will also contain a vignette that will be used to demonstrate the use of the functions in the package.

## Installation

You can install the development version of hcesR2 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("dzvoti/hcesR")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(hcesR)
```
